Concurrent Programming with CXL

### 2020-06-16 book/paper.tex
Glossary now in table of contents
Still more index terms

\documentclass{report}
\usepackage{fullpage}
\usepackage{imakeidx}\makeindex
\usepackage{hyperref}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage{glossaries}\makeglossaries
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}

@@

(For this to work, make sure \texttt{cxl} is in your command shell's search path.)
Essentially, the $\texttt{choose}(S)$
operator provides the input to the program by selecting some value from the
set~$S$, while the $\texttt{assert}$ statement checks that the output is
correct.  If the program is correct, the output of CXL is the size of the
``state graph'' (13 states in this case).  If not, CXL also
reports what went wrong, typically by displaying a summary of an execution in
which something went wrong.

In CXL, constants have a default, but those can be overridden on the command
line using the \texttt{-c} option.
For example, if you want to test the code for \texttt{N = 100}, run:
\begin{code}
\begin{verbatim}
$ cxl -c N=100 triangle.cxl
#states = 103
no issues found
$
\end{verbatim}
\end{code}

@@

Figure~\ref{fig:petersonmethods} again shows Peterson's algorithm,
but this time with methods defined to enter and exit the critical
section.
You can put the first three methods in its own CXL source file
and include it using the CXL \texttt{import} statement.  This would
make the code re-usable by other applications.  For those who are
extra adventurous: you can add the \texttt{P\_enter} and
\texttt{P\_exit} methods to the \texttt{P\_mutex} dictionary
like so:
\begin{code}
\begin{verbatim}
dict{ .turn: 0, .flags: [ False, False ], .enter: P_enter, .exit: P_exit }
\end{verbatim}
\end{code}
That would allow you to simulate object methods.

@@

CXL allows you to select which version of the \texttt{synch} module you would
like to use with the \texttt{-m} flag.  For example,

>>>>

\documentclass{report}
\usepackage{fullpage}
\usepackage{imakeidx}\makeindex
\usepackage{hyperref}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage[toc]{glossaries}\makeglossaries
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}

@@

(For this to work, make sure \texttt{cxl} is in your command shell's search path.)
Essentially, the $\texttt{choose}(S)$
\index{choose operator}
operator provides the input to the program by selecting some value from the
set~$S$, while the $\texttt{assert}$ statement checks that the output is
correct.  If the program is correct, the output of CXL is the size of the
``state graph'' (13 states in this case).  If not, CXL also
reports what went wrong, typically by displaying a summary of an execution in
which something went wrong.

In CXL, constants have a default, but those can be overridden on the command
line using the \texttt{-c} option.
\index{constant}
For example, if you want to test the code for \texttt{N = 100}, run:
\begin{code}
\begin{verbatim}
$ cxl -c N=100 triangle.cxl
#states = 103
no issues found
$
\end{verbatim}
\end{code}

@@

Figure~\ref{fig:petersonmethods} again shows Peterson's algorithm,
but this time with methods defined to enter and exit the critical
section.
You can put the first three methods in its own CXL source file
and include it using the CXL \texttt{import} statement.
\index{import statement}
\index{module}
This would
make the code re-usable by other applications.  For those who are
extra adventurous: you can add the \texttt{P\_enter} and
\texttt{P\_exit} methods to the \texttt{P\_mutex} dictionary
like so:
\begin{code}
\begin{verbatim}
dict{ .turn: 0, .flags: [ False, False ], .enter: P_enter, .exit: P_exit }
\end{verbatim}
\end{code}
That would allow you to simulate object methods.

@@

CXL allows you to select which version of the \texttt{synch} module you would
like to use with the \texttt{-m} flag.
\index{module}
For example,
